---
output: github_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

## iCTC: identification of circulating tumor cells

The goal of iCTC is to detect whether peripheral blood cells have CTCs
(circulating tumor cell) or not.

## Installation

You can install the released version of iCTC from
[CRAN](https://CRAN.R-project.org) with:

``` r
install.packages('iCTC')
```
or can also be download through below commands 

``` r
library(devtools)
install_github('krishan57gupta/iCTC')
```

## Vignette tutorial

This vignette uses a small dataset of cell samples, which is saved in package itself, to demonstrate a standard pipeline. This vignette can be used as a tutorial as well.

Libraries need to be loaded before running iCTC.

```{r setuplib}
library(iCTC)
library(harmony)
```

```{r data, message=FALSE,warning = FALSE,include=TRUE, cache=FALSE}
cell_samples=iCTC::raw_test_data$Clearcell_Polaris_sample_test
head(cell_samples)
```


```{r main, message=FALSE,warning = FALSE, include=TRUE, cache=FALSE}
results<-iCTC(cell_samples=cell_samples, cases = c(1:9))
```

```{r output, message=FALSE,warning = FALSE,include=TRUE, cache=FALSE}
results
```
