---
title: "iCTC"
output: rmarkdown::html_vignette
vignette: >
    %\VignetteIndexEntry{iCTC}
    %\VignetteEngine{knitr::rmarkdown}
    %\VignetteEncoding{UTF-8}
---

```{r first, include = FALSE}
knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>"
)
```

## iCTC: identification of circulating tumor cells

The goal of iCTC is to detect whether peripheral blood cells have CTCs
(circulating tumor cell) or not.

## Installation

The developer version of the R package can be installed 
with the following R commands:

``` r
if (!requireNamespace("BiocManager", quietly = TRUE))
    install.packages("BiocManager")
BiocManager::install('iCTC')
```
or can be installed with the following R commands:

``` r
library(devtools)
install_github("immunogenomics/harmony")
install_github('krishan57gupta/iCTC')
```

## Vignette tutorial

This vignette uses a small dataset of cell samples, 
which is saved in package itself, to demonstrate a standard pipeline. 
This vignette can be used as a tutorial as well.

Libraries need to be loaded before running iCTC.

```{r setuplib}
library(iCTC)
```
```{r data, message=FALSE,warning = FALSE,include=TRUE, cache=FALSE}
cell_samples=iCTC::raw_test_data$Clearcell_Polaris_sample_test
head(cell_samples)
```


```{r main, message=FALSE,warning = FALSE, include=TRUE, cache=FALSE}
results<-iCTC(cell_samples=cell_samples, cases = seq_len(3))
```

```{r output, message=FALSE,warning = FALSE,include=TRUE, cache=FALSE}
results
```
